---
site: workflowr::wflow_site
title: "Effect of Probiotic"
author: "Marc Noguera-Julian, PhD. TreeTopUnder"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
header-includes:
- \usepackage{fancyhdr}
- \usepackage{lipsum}
- \pagestyle{fancy}
- \fancyhead[CO,CE]{2022-PurinaLeish-WMGS}
- \fancyfoot[LO,RE]{Marc Noguera-Julian, TreeTopUnder}
- \fancyhead[LE,RO]{\thepage}
- \fancyfoot[CO,CE]{}
- \usepackage[default]{sourcesanspro}
- \usepackage[T1]{fontenc}
- \usepackage{eso-pic,graphicx,transparent}
mainfont: Helvetica
output: html_document
---

```{r setup, include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())
bifido_animals<-c("RUDDY","NANI","LEO","BALOO")
set.seed(1234)
```


The goal of this part of the analysis is to assess the effect of supplementing dogs’ diet with probiotics, after GlucanTime treatment interruption, at the taxonomic and functional level. For that, only M1 and M4 samples will be used, in a animal paired manner, to characterized differences at the taxonomical and functional level, separately for the Probiotic and Placebo groups. Note: sample sizes for each of the groups (n=5) are very low and have limited statistical power due to under-recruitment at the clinical stage. _Results may be affected_.


## Alpha Diversity

We want to see if alpha-diversity is differentially affected in those dog within the Probiotic group with respect to those dogs receiving placebo. For that we will use gene richness parameter. First we want to see if there is any overall trend in changes of alpha-diversity parameters, using all dogs, between M4 and M1. Results indicate that there is no significant increase or decrease, although it seems that there is a in increase trend that consistently affects all three parameters.

*Deliverables: AlphaDiversity_Timepoint_goal2_all_samples.pdf*

```{r alpha diversity chunk1, include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F}
suppressMessages(require(phyloseq))
suppressMessages(require(patchwork))
suppressMessages(require(dplyr))

ps_metaphlan<-readRDS("data/processed/ps_metaphlan_goal2_sec.rds")
my_datatable<-readRDS("data/raw/CatalogMapping/IGC/dataTable.rds")
mymin<-min(my_datatable$NumberMappedReads) #
my_datatable<-my_datatable %>% 
  dplyr::filter(ReadCountReal==6000000) %>% 
  dplyr::filter(SampleID %in% phyloseq::sample_data(ps_metaphlan)$SampleID) %>% 
  dplyr::select(SampleID,GeneNumber)

x.2.0 <-ps_metaphlan
x.2.0.species<-x.2.0

plot_data<-phyloseq::estimate_richness(x.2.0.species) %>% 
  tibble::rownames_to_column() %>% 
  dplyr::mutate(rowname=gsub("X","",rowname)) %>% 
  dplyr::left_join(phyloseq::sample_data(ps_metaphlan) %>% data.frame(),by=c("rowname"="SampleID")) %>% 
  dplyr::rename(SampleID=rowname) %>% 
  dplyr::select(SampleID, Timepoint, Host_name, Chao1,Shannon) %>% 
  dplyr::left_join(my_datatable,by="SampleID") %>% 
  reshape2::melt() 

p0<-
  plot_data %>% 
  dplyr::arrange(Host_name) %>% 
  dplyr::group_by(Host_name,variable) %>% 
  ggstatsplot::grouped_ggwithinstats(x=Timepoint,y=value,grouping.var = variable,type="non-parametric",centrality.plotting=F,
                                      annotation.args = list(title = "M4 vs M1 | All Samples",
                                                         theme = ggplot2::theme(
                                                                plot.subtitle = ggplot2::element_text(size = 13),
                                                                plot.title = ggplot2::element_text(size = 14)
                                                                )
                                                         ),
                                  plotgrid.args = list(nrow = 3))
p0
# pT<- p0 / p1 / p2
ggplot2::ggsave(p0,filename="output/Deliverables/Goal2/AlphaDiversity/AlphaDiversity_Timepoint_goal2_all_samples.pdf",height=15,width=7)
# ggplot2::ggsave(p1,filename="output/Deliverables/AlphaDiversity_treatment_w1_only.pdf",height=15,width=7)
# ggplot2::ggsave(p2,filename="output/Deliverables/AlphaDiversity_treatment_w2_only.pdf",height=15,width=7)
# ggplot2::ggsave(pT,filename="output/Deliverables/AlphaDiversity_treatment.pdf",height=15,width=7)
```

### Probiotic vs Placebo

We are interested in knowing whether changes in alpha-diversity exist in any of the Probiotic/Placebo groups, separately. REsults indicate that there are no significant changes in Chao1, Shannon or Gene Richness in any of the groups, with similar trend than in the global analysis.

*Deliverables: AlphaDiversity_Timepoint_goal2_Probiotic_samples.pdf, AlphaDiversity_Timepoint_goal2_Placebo_samples.pdf*

```{r alpha diversity chunk2, include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F}
suppressMessages(require(phyloseq))
suppressMessages(require(patchwork))
suppressMessages(require(dplyr))

ps_metaphlan<-readRDS("data/processed/ps_metaphlan_goal2_sec.rds")
my_datatable<-readRDS("data/raw/CatalogMapping/IGC/dataTable.rds")
mymin<-min(my_datatable$NumberMappedReads) #
my_datatable<-my_datatable %>% 
  dplyr::filter(ReadCountReal==6000000) %>% 
  dplyr::filter(SampleID %in% phyloseq::sample_data(ps_metaphlan)$SampleID) %>% 
  dplyr::select(SampleID,GeneNumber)

x.2.0 <- ps_metaphlan
x.2.0.species<-x.2.0

plot_data<-phyloseq::estimate_richness(x.2.0.species) %>% 
  tibble::rownames_to_column() %>% 
  dplyr::mutate(rowname=gsub("X","",rowname)) %>% 
  dplyr::left_join(sample_data(ps_metaphlan) %>% data.frame(),by=c("rowname"="SampleID")) %>% 
  dplyr::mutate(Treatment=ifelse(grepl(848590,Product),"Probiotic","Placebo")) %>% 
  dplyr::rename(SampleID=rowname) %>% 
  dplyr::select(SampleID, Timepoint, Treatment,Host_name, Chao1,Shannon) %>% 
  dplyr::left_join(my_datatable,by="SampleID") %>% 
  reshape2::melt() 

p0<-
  plot_data %>% 
  dplyr::filter(Treatment=="Probiotic") %>% 
  dplyr::arrange(Host_name) %>% 
  dplyr::group_by(Host_name,variable) %>% 
  ggstatsplot::grouped_ggwithinstats(x=Timepoint,y=value,grouping.var = variable,type="non-parametric",centrality.plotting=F,
                                      annotation.args = list(title = "M4 vs M1 | Probiotic Samples",
                                                         theme = ggplot2::theme(
                                                                plot.subtitle = ggplot2::element_text(size = 13),
                                                                plot.title = ggplot2::element_text(size = 14)
                                                                )
                                                         ),
                                  plotgrid.args = list(nrow = 3))

p1<-
  plot_data %>% 
  dplyr::filter(Treatment=="Placebo") %>% 
  dplyr::arrange(Host_name) %>% 
  dplyr::group_by(Host_name,variable) %>% 
  ggstatsplot::grouped_ggwithinstats(x=Timepoint,y=value,grouping.var = variable,type="non-parametric",centrality.plotting=F,
                                      annotation.args = list(title = "M4 vs M1 | Placebo Samples",
                                                         theme = ggplot2::theme(
                                                                plot.subtitle = ggplot2::element_text(size = 13),
                                                                plot.title = ggplot2::element_text(size = 14)
                                                                )
                                                         ),
                                  plotgrid.args = list(nrow = 3))
p0
p1
# pT<- p0 / p1 / p2
ggplot2::ggsave(p0,filename="output/Deliverables/Goal2/AlphaDiversity/AlphaDiversity_Timepoint_goal2_Probiotic_samples.pdf",height=15,width=7)
ggplot2::ggsave(p1,filename="output/Deliverables/Goal2/AlphaDiversity/AlphaDiversity_Timepoint_goal2_Placebo_samples.pdf",height=15,width=7)
# ggplot2::ggsave(p1,filename="output/Deliverables/AlphaDiversity_treatment_w1_only.pdf",height=15,width=7)
# ggplot2::ggsave(p2,filename="output/Deliverables/AlphaDiversity_treatment_w2_only.pdf",height=15,width=7)
# ggplot2::ggsave(pT,filename="output/Deliverables/AlphaDiversity_treatment.pdf",height=15,width=7)
```

## Beta Diversity

Aside from alpha-diversity we are interested in changes in the composition of the dog's gut microbiome after Probiotic/Placebo treatment. Of course, there is some degree of change in the compisition, but we are interested if these changes are significantly different when comparing Probiotic and Placebo group.

### Ordination Analysis

We will use the same ordination method than in previous exploratory section but, in this case, only applied to M1 and M4 samples to detect significant changes related to the effect of Allopurinol + Glucantime treatment, discarding the effect of other variables that may act as confounders.

*Deliverables: Goal2/BetaDiversity/NMDS_Ordination_vs_Timepoint.pdf, Goal2/BetaDiversity/NMDS_Goal2_StressPlot.pdf, Goal2/BetaDiversity/Goal2_Adonis.xls*

Results: There is no apparent clustering among M1 or M4 samples,  nor among samples from dogs receiving Probiotic or Placebo. Here, we are assuming product "848590" is the one receiving Probiotic, according to the findings of the exploratory results on *E. faecium*. PERMANOVA results also indicate no significant effect of Timepoint or treatment in this dataset while, as expected, dog identity variable explains more than 70% of microbiome composition on this subset of samples.

```{r Global Ordination Beta Diversity chunk 3, include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F}
suppressWarnings(require(phyloseq))
suppressWarnings(require(dplyr))
suppressWarnings(require(ggplot2))
suppressWarnings(require(ggforce))
suppressWarnings(require(patchwork))
set.seed(1234)

x.2.0<-readRDS("data/processed/ps_metaphlan_goal2_sec.rds")
set.seed(1234)
x.2.0.species<-x.2.0
x.2.0.species<-transform_sample_counts(x.2.0.species, function(x) ((x/sum(x))))
sampleData<-data.frame(sample_data(x.2.0.species))
rownames(sampleData)<-sampleData$SampleID
sampleData<-sampleData %>% 
  dplyr::mutate(Treatment=ifelse(grepl(848590,Product),"Probiotic","Placebo"))  
sample_data(x.2.0.species)<-sampleData
capture.output(myOrd<-phyloseq::ordinate(x.2.0.species,method="NMDS",distance="bray",trymax=100),file="/dev/null")

pdf("output/Deliverables/Goal2/BetaDiversity/NMDS_Goal2_StressPlot.pdf")
vegan::stressplot(myOrd)
dev.off()

#### PERMUTATIONAL ANOVA (adonis()) on Bray-Curtus distance
x.6.0.explanatory<-sampleData[,c("Timepoint","SampleID","Host_name","Treatment")]
x.6.0.response<-phyloseq::distance((x.2.0.species),method="bray")
myAdonis<-vegan::adonis2(x.6.0.response~Treatment,data=x.6.0.explanatory)
file.remove("output/Deliverables/Goal2/BetaDiversity/Goal2_Adonis.xls")
xlsx::write.xlsx(file = "output/Deliverables/Goal2/BetaDiversity/Goal2_Adonis.xls",sheetName = "Timepoint",vegan::adonis2(x.6.0.response~Timepoint,data=x.6.0.explanatory))
### Perform ANOVA for non-NA in treatment
xlsx::write.xlsx(file = "output/Deliverables/Goal2/BetaDiversity/Goal2_Adonis.xls",sheetName = "Host_name",vegan::adonis2(x.6.0.response~Host_name,data=x.6.0.explanatory),append=T)
### Perform ANOVA for non-NA in treatment
xlsx::write.xlsx(file = "output/Deliverables/Goal2/BetaDiversity/Goal2_Adonis.xls",sheetName = "Treatment",vegan::adonis2(x.6.0.response~Treatment,data=x.6.0.explanatory),append=T)


### By Timepoint
p0<-plot_ordination(x.2.0.species,
                    myOrd,
                    color = "Timepoint",
                    shape="Treatment") + 
  geom_point(size=5) +
  ggtitle("Unconstrained NMDS(Bray) by Timepoint")+
  theme_classic() +
  stat_ellipse(alpha=1,lwd = 1.2,
               mapping=aes(color=Timepoint),na.rm = T)+
  labs(x = "NMDS Dimension 1", y = "NMDS Dimension 2") + 
        guides(fill = guide_legend(override.aes = list(size = 4)))+ 
    theme(plot.title = element_text(size = 12, face = "bold"))+
    scale_color_brewer(palette="Dark2")
p0
ggsave(plot=p0,filename="output/Deliverables/Goal2/BetaDiversity/NMDS_Ordination_vs_Timepoint_and_treatment.pdf",height=5,width=5)

```

In order to have some more granular view of differences, at the ordination level, we'll check if paired Beta-Diversity  between M1 and M4 samples from the same animals are differen between the Probiotic and Placebo treatment groups. Results indicate no differential change between Probiotic and Placebo groups.

*Deliverables: Goal2/BetaDiversity/BrayDistance_by_Treatment_goal2.pdf*

```{r Global Ordination Beta Diversity chunk 4, include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F}
suppressWarnings(require(phyloseq))
suppressWarnings(require(dplyr))
suppressWarnings(require(ggplot2))
suppressWarnings(require(ggforce))
suppressWarnings(require(patchwork))
set.seed(1234)

x.2.0<-readRDS("data/processed/ps_metaphlan_goal2_sec.rds")
set.seed(1234)
x.2.0.species<-x.2.0
x.2.0.species<-transform_sample_counts(x.2.0.species, function(x) ((x/sum(x))))
sampleData<-data.frame(sample_data(x.2.0.species))
rownames(sampleData)<-sampleData$SampleID
sampleData<-sampleData %>% 
  dplyr::mutate(Treatment=ifelse(grepl(848590,Product),"Probiotic","Placebo"))  
sample_data(x.2.0.species)<-sampleData
# suppressWarnings(myOrd<-phyloseq::ordinate(x.2.0.species,method="NMDS",distance="bray",trymax=100))

p0<-phyloseq::distance(x.2.0.species,method = "bray") %>% 
  as.matrix() %>% reshape::melt() %>% 
  dplyr::rename(Sample1=X1,Sample2=X2) %>% 
  dplyr::left_join(sampleData %>% dplyr::select(SampleID,Host_name),by=c("Sample1"="SampleID")) %>% 
  dplyr::rename(Host_name1=Host_name) %>% 
  dplyr::left_join(sampleData %>% dplyr::select(SampleID,Host_name),by=c("Sample2"="SampleID")) %>% 
  dplyr::rename(Host_name2=Host_name) %>% 
  dplyr::filter(Host_name1==Host_name2) %>% 
  dplyr::filter(Sample1 != Sample2) %>% 
  dplyr::select(-Sample1, -Sample2, -Host_name2) %>%
  dplyr::rename(Host_name=Host_name1) %>% 
  dplyr::left_join(sampleData %>% ungroup() %>%  dplyr::select(Host_name,Treatment)) %>% 
  unique() %>% 
  dplyr::rename(Distance=value) %>% 
  ggstatsplot::ggbetweenstats(Treatment, Distance, title="Probiotic: Paired Distance vs Treatment",bf.message=F,type="np")
p0
ggsave(p0,filename = "output/Deliverables/Goal2/BetaDiversity/BrayDistance_by_Treatment_goal2.pdf")
```

## Differential Abundance

We are interested in seeing whether there is any differentially abundant species between M4 and M1 in any of the groups. Low group sizes (n=5 for Probiotic and n=5 for Placebo) greatly reduce the statistical power to detect any, but we'll try anyway. We will use both LefseR and MaasLin models. 

### Lefse

LEFsE results shows for the probiotic group, an increase in M4, of three different species:  *Blautia*, *Clostridium* and *Dorea* CAGs. A CAG is a co-abundant-group that has been obtained from metagnomic data (thus not cultivated) and whose taxonomical annotation is limited in resolution and in reliability.
In the Placebo Group, there are also two species that show to be significantly more abundant in M4, although they received no Probiotic: *Collinsella Intestinallis* and *Clostridium hiranonis*.
Note that Lefse test does not use dog id as pairing variable. Using dog id is a formally more correct way to perform the testing, since it accounts for inter-doc variability. Actually, when individual paired rank-sum Wilcoxon paired tests are applied to this data, for each of the species obtained from LEFsE, significance is lost for all of the LEFsE-positive species.

#### Probiotic Group

We will perform LEFsE test for the probiotic group samples only, comparing M4 and M1 samples. Note that as in goal 1 analysis, LEFsE does not using dog id as a pairing variable, and results need to be checked using paired-wilcoxon afterwards.

*Deliverables: Goal2/DifferentialAbundance/lefse/lefser_goal2_Probiotic_plot.pdf, Goal2/DifferentialAbundance/lefse/boxplots/Species_vs_Timepoint_Probiotic_Goal2.pdf, Goal2/DifferentialAbundance/lefse/boxplots/paired_Species_vs_Timepoint_Probiotic_Goal2.pdf*

```{r Timepoint DA chunk1 Species, include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F,eval=T}
suppressMessages(require(dplyr))
suppressMessages(require(phyloseq))
suppressMessages(require(lefser))
suppressMessages(require(ggplot2))
suppressMessages(require(patchwork))

set.seed(1234)
### Species Level

x.2.0<-readRDS("data/processed/ps_metaphlan_goal2_sec.rds")
set.seed(1234)
x.2.0.species<-x.2.0

### Species Level for Probiotic
x.2.0 <-x.2.0.species %>% 
  phyloseq::subset_samples(Product=="848590-FR80-036-003") ## Probiotic
se_ps<-SummarizedExperiment::SummarizedExperiment(assays = list(counts=as.matrix(otu_table(x.2.0))),
                                                  colData=sample_data(x.2.0),
                                                  rowData=tax_table(x.2.0))
aux_res<-lefser(expr=se_ps,groupCol="Timepoint",blockCol = NULL,lda.threshold = 1,)
aux_res<-merge(aux_res,tax_table(x.2.0),by.x="Names",by.y="row.names")%>% 
  dplyr::select(Names,Phylum,Class,Order,Family,Genus,Species,scores) %>% 
  dplyr::mutate(Class=ifelse(is.na(Class),Phylum,Class)) %>% 
  dplyr::mutate(Order=ifelse(is.na(Order),Class,Order)) %>% 
  dplyr::mutate(Family=ifelse(is.na(Family),Order,Family)) %>% 
  dplyr::mutate(Genus=ifelse(is.na(Genus),Family,Genus)) %>% 
  dplyr::mutate(Species=ifelse(is.na(Species),paste0(Genus,"_spp"),Species)) %>% 
  dplyr::filter(! is.na(Species)) %>% 
  dplyr::mutate(otu=Names) %>% 
  dplyr::mutate(Names=Species) %>% 
  dplyr::select(otu,Names,scores) %>% 
  dplyr::mutate(Names = forcats::fct_reorder(Names, scores)) %>% 
  dplyr::mutate(Timepoint=ifelse(scores>0,"M4","M1"))
p0<-aux_res %>% 
    ggplot(.,aes(x=Names,y=scores,fill=Timepoint))+geom_bar(stat="identity")+coord_flip()+
    theme_classic()+ggtitle("Month4 vs Month1")+
    scale_fill_brewer(palette="Dark2")
p0
ggsave(p0,filename = "output/Deliverables/Goal2/DifferentialAbundance/lefse/lefser_goal2_Probiotic_plot.pdf")
for(otu_name in aux_res$otu){
  my_ps <- x.2.0 
  title <- aux_res %>% 
    dplyr::filter(otu==otu_name) 
  my_ps %>% 
  phyloseq::psmelt()%>% 
  dplyr::filter(OTU==otu_name) %>% 
  dplyr::arrange(Host_name) %>% 
  ggstatsplot::ggbetweenstats(data = .,x=Timepoint,y=Abundance,
                                      type = "nonparametric",
                                      pairwise.comparisons = FALSE,
                                      xlab="Timepoint",ylab="Counts",centrality.plotting=F,
                                      bf.message=F,title=title$Names,outlier.label=Host_name,
                                      palette="Dark2") %>% 
  ggsave(.,filename=paste0("output/Deliverables/Goal2/DifferentialAbundance/lefse/boxplots/",title$Names,"_vs_Timepoint_Probiotic_Goal2.pdf"),width=7, height=7)
  my_ps %>% 
  phyloseq::psmelt()%>% 
  dplyr::filter(OTU==otu_name) %>% 
  dplyr::arrange(Host_name) %>% 
  ggstatsplot::ggwithinstats(data = .,x=Timepoint,y=Abundance,
                                      type = "nonparametric",
                                      pairwise.comparisons = TRUE,
                                      xlab="Timepoint",ylab="Counts",centrality.plotting=F,
                                      bf.message=F,title=title$Names,
                                      palette="Dark2") %>% 
   ggsave(.,filename=paste0("output/Deliverables/Goal2/DifferentialAbundance/lefse/boxplots/paired_",title$Names,"_vs_Timepoint_Probiotic_Goal2.pdf"),width=7, height=7)
}
```

#### Placebo Group


*Deliverables: Goal2/DifferentialAbundance/lefse/lefser_goal2_Placebo_plot.pdf, Goal2/DifferentialAbundance/lefse/boxplots/Species_vs_Timepoint_Placebo_Goal2.pdf, Goal2/DifferentialAbundance/lefse/boxplots/paired_Species_vs_Timepoint_Placebo_Goal2.pdf*

```{r Timepoint DA chunk2 Species, include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F,eval=T}
suppressMessages(require(dplyr))
suppressMessages(require(phyloseq))
suppressMessages(require(lefser))
suppressMessages(require(ggplot2))
suppressMessages(require(patchwork))

set.seed(1234)
### Species Level
### Species Level for Placebo
x.2.0<-readRDS("data/processed/ps_metaphlan_goal2_sec.rds")
set.seed(1234)
x.2.0.species<-x.2.0
x.2.0 <-x.2.0.species %>% 
  phyloseq::subset_samples(Product=="848589-FR80-036-003") ## Placebo
flist    <- genefilter::filterfun(genefilter::kOverA(1, 1))
x.2.0<-phyloseq::filter_taxa(x.2.0,flist,TRUE)

se_ps<-SummarizedExperiment::SummarizedExperiment(assays = list(counts=as.matrix(otu_table(x.2.0))),
                                                  colData=sample_data(x.2.0),
                                                  rowData=tax_table(x.2.0))
aux_res<-lefser(expr=se_ps,groupCol="Timepoint",blockCol = NULL,lda.threshold = 1,)
aux_res<-merge(aux_res,tax_table(x.2.0),by.x="Names",by.y="row.names")%>% 
  dplyr::select(Names,Phylum,Class,Order,Family,Genus,Species,scores) %>% 
  dplyr::mutate(Class=ifelse(is.na(Class),Phylum,Class)) %>% 
  dplyr::mutate(Order=ifelse(is.na(Order),Class,Order)) %>% 
  dplyr::mutate(Family=ifelse(is.na(Family),Order,Family)) %>% 
  dplyr::mutate(Genus=ifelse(is.na(Genus),Family,Genus)) %>% 
  dplyr::mutate(Species=ifelse(is.na(Species),paste0(Genus,"_spp"),Species)) %>% ## Placebo
  dplyr::filter(! is.na(Species)) %>% 
  dplyr::mutate(otu=Names) %>% 
  dplyr::mutate(Names=Species) %>% 
  dplyr::select(otu,Names,scores) %>% 
  dplyr::mutate(Names = forcats::fct_reorder(Names, scores)) %>% 
  dplyr::mutate(Timepoint=ifelse(scores>0,"M4","M1"))
p1<-aux_res %>% 
    ggplot(.,aes(x=Names,y=scores,fill=Timepoint))+geom_bar(stat="identity")+coord_flip()+
    theme_classic()+ggtitle("Month4 vs Month1 | Placebo")+## Placebo
    scale_fill_brewer(palette="Dark2")

ggsave(p1,filename = "output/Deliverables/Goal2/DifferentialAbundance/lefse/lefser_goal2_Placebo_plot.pdf")
for(otu_name in aux_res$otu){
  my_ps <- x.2.0 
  title <- aux_res %>% 
    dplyr::filter(otu==otu_name) 
  my_ps %>% 
  phyloseq::psmelt()%>% 
  dplyr::filter(OTU==otu_name) %>% 
  dplyr::arrange(Host_name) %>% 
  ggstatsplot::ggbetweenstats(data = .,x=Timepoint,y=Abundance,
                                      type = "nonparametric",
                                      pairwise.comparisons = FALSE,
                                      xlab="Timepoint",ylab="Counts",centrality.plotting=F,
                                      bf.message=F,title=title$Names,outlier.label=Host_name,
                                      palette="Dark2") %>% 
  ggsave(.,filename=paste0("output/Deliverables/Goal2/DifferentialAbundance/lefse/boxplots/",title$Names,"_vs_Timepoint_Placebo_Goal2.pdf"),width=7, height=7)
  my_ps %>% 
  phyloseq::psmelt()%>% 
  dplyr::filter(OTU==otu_name) %>% 
  dplyr::arrange(Host_name) %>% 
  ggstatsplot::ggwithinstats(data = .,x=Timepoint,y=Abundance,
                                      type = "nonparametric",
                                      pairwise.comparisons = TRUE,
                                      xlab="Timepoint",ylab="Counts",centrality.plotting=F,
                                      bf.message=F,title=title$Names,
                                      palette="Dark2") %>% 
   ggsave(.,filename=paste0("output/Deliverables/Goal2/DifferentialAbundance/lefse/boxplots/paired_",title$Names,"_vs_Timepoint_Placebo_Goal2.pdf"),width=7, height=7)
}


```

### MaasLin2

MaasLin2 used generalized linear models to better fit microbiome data distribution and to improve sensitivity/specificity. In addition, MaasLin method allows for the accounting of other variables in the test desing. In particular, we can use dog name variable(*Host_name*) as a random effect, while *Timepoint*(M4 vs M1) is used as a fixed effect.e


Results: Using MaasLin2 there are no significant hits at species nor genus level for neither of the Probiotic or Placebo groups when using BH-corrected qvalues, thus confirming the previous results by paired Wilcoxon tests. However, if using non-corrected p.values, we can see that *Blautia_sp_CAG_257* and *Dorea_sp_CAG_317* do increase in the probotic group, while *Blautia_hansenii* and *Firmicutes_bacterium_CAG_424* increase in the placebo group. Thus, there is an overlap in differentially abundant species for the probiotic group, reinforcing the plausibility of the increase abundance of these species, although formally the signal is non-significant.

#### Probiotic group

*Deliverables: Goal2/DifferentialAbundance/maaslin/Taxa_M4_vs_M1_probiotic.xlsx, Goal2/DifferentialAbundance/maaslin/Taxa_M4_vs_M1_placebo.xlsx*

```{r DA species maaslin2 chunk 1, include=TRUE, echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=T,eval=T}
suppressMessages(require(dplyr))
suppressMessages(require(phyloseq))
suppressMessages(require(lefser))
suppressMessages(require(ggplot2))
suppressMessages(require(patchwork))
suppressMessages(require(Maaslin2))

set.seed(1234)
### Species Level
### Probiotic
x.2.0<-readRDS("data/processed/ps_metaphlan_goal2.rds")
set.seed(1234)
x.2.0.species<-x.2.0 %>% 
  phyloseq::subset_samples(Product=="848590-FR80-036-003")
tax_df<-tax_table(x.2.0.species) %>% data.frame() %>%  dplyr::select(Species) %>% tibble::rownames_to_column("feature")
# tax_df$feature<-rownames(x.2.0.species)

input_data<-x.2.0.species %>% otu_table() %>% t()

input_metadata <- phyloseq::sample_data(x.2.0.species) %>% data.frame()
rownames(input_metadata)<-input_metadata$SampleID
if( file.exists("output/Deliverables/Goal2/DifferentialAbundance/maaslin/species_probiotic.rds")){
  fit_data<-readRDS("output/Deliverables/Goal2/DifferentialAbundance/maaslin/species_probiotic.rds")
}else{
  suppressWarnings(fit_data <- Maaslin2::Maaslin2(input_data=input_data,input_metadata=input_metadata,output="output/Deliverables/Goal2/DifferentialAbundance/maaslin/species_probiotic",fixed_effects = c("Timepoint"),random_effects = c("Host_name"),cores=4)) ### No siginifcant hits
  saveRDS(fit_data,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/species_probiotic.rds")
}
plot_data<-fit_data$results %>% 
  dplyr::mutate('-log(qval)'=-log10(qval)) %>% 
  dplyr::mutate(significant=ifelse(qval<0.05,"q<0.05","ns")) %>% 
  dplyr::mutate(labels=ifelse(significant=="ns",FALSE,TRUE)) %>% 
  dplyr::mutate(feature=ifelse(significant=="ns","",feature)) 
  
p0<-ggplot(plot_data)+
    geom_point(aes(x=coef,y=`-log(qval)`,color=significant))+
    ggrepel::geom_text_repel(aes(x=coef,y=`-log(qval)`),size=2,
                                 label = plot_data$feature,max.overlaps = 30,
                                 box.padding = unit(0.25, "lines"),
                                  hjust = 1)+
    ggtitle("M4 vs M1 | Species/Probiotic")
fit_data$results %>% 
  dplyr::left_join(tax_df) %>% 
  dplyr::select(-feature, -name) %>% 
  dplyr::relocate(Species,.before = metadata) %>%
  dplyr::arrange(pval) %>%  head() %>% knitr::kable()
file.remove("output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_probiotic_Taxa.xlsx")
fit_data$results %>% 
  dplyr::left_join(tax_df) %>% 
  dplyr::select(-feature, -name) %>% 
  dplyr::relocate(Species,.before = metadata) %>% 
  xlsx::write.xlsx(.,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_probiotic_Taxa.xlsx",sheetName = "Species")

p0
### Genus Level
input_data<-x.2.0.species %>% tax_glom(.,taxrank="Genus",NArm = F) %>% otu_table() %>% t()
input_metadata<-x.2.0.species %>% tax_glom(.,taxrank="Genus",NArm = F) %>% phyloseq::sample_data() %>% data.frame()
rownames(input_metadata)<-input_metadata$SampleID
tax_df<-tax_table(x.2.0.species %>% 
                    tax_glom(.,taxrank="Genus",NArm = F)) %>% 
  data.frame() %>%  dplyr::select(Genus) %>% 
  tibble::rownames_to_column("feature")
# rownames(input_metadata)
if( file.exists("output/Deliverables/Goal2/DifferentialAbundance/maaslin/genus_probiotic.rds")){
  fit_data<-readRDS("output/Deliverables/Goal2/DifferentialAbundance/maaslin/genus_probiotic.rds")
}else{
  suppressWarnings(fit_data <- Maaslin2::Maaslin2(input_data=input_data,input_metadata=input_metadata,output="output/Deliverables/Goal2/DifferentialAbundance/maaslin/genus_probiotic",fixed_effects = c("Timepoint"),random_effects = c("Host_name"),cores=4)) ### No siginifcant hits
  saveRDS(fit_data,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/genus_probiotic.rds")
}
fit_data$results %>% 
  dplyr::left_join(tax_df) %>% 
  dplyr::select(-feature, -name) %>% 
  dplyr::relocate(Genus,.before = metadata) %>% 
  xlsx::write.xlsx(.,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_probiotic_Taxa.xlsx",sheetName = "Genus",append = T)

```

#### Placebo group

```{r DA species maaslin2 chunk 2, include=TRUE, echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=T,eval=T}
suppressMessages(require(dplyr))
suppressMessages(require(phyloseq))
suppressMessages(require(lefser))
suppressMessages(require(ggplot2))
suppressMessages(require(patchwork))
suppressMessages(require(Maaslin2))

set.seed(1234)
### Placebo
x.2.0<-readRDS("data/processed/ps_metaphlan_goal2.rds")
set.seed(1234)
x.2.0.species<-x.2.0 %>% 
  phyloseq::subset_samples(Product=="848589-FR80-036-003")
tax_df<-tax_table(x.2.0.species) %>% as.data.frame() %>%  dplyr::select(Species) %>% tibble::rownames_to_column("feature")
# tax_df$feature<-rownames(x.2.0.species)
input_data<-x.2.0.species %>% otu_table() %>% t()

input_metadata<-sample_data(x.2.0.species) %>% data.frame()
rownames(input_metadata)<-input_metadata$SampleID
if( file.exists("output/Deliverables/Goal2/DifferentialAbundance/maaslin/species_placebo.rds")){
  fit_data<-readRDS("output/Deliverables/Goal2/DifferentialAbundance/maaslin/species_placebo.rds")
}else{
  suppressWarnings(fit_data <- Maaslin2::Maaslin2(input_data=input_data,input_metadata=input_metadata,output="output/Deliverables/Goal2/DifferentialAbundance/maaslin/species_Placebo",fixed_effects = c("Timepoint"),random_effects = c("Host_name"),cores=4)) ### No siginifcant hits
   saveRDS(fit_data,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/species_placebo.rds")
}
plot_data<-fit_data$results %>% 
  dplyr::mutate('-log(qval)'=-log10(qval)) %>% 
  dplyr::mutate(significant=ifelse(qval<0.05,"q<0.05","ns")) %>% 
  dplyr::mutate(labels=ifelse(significant=="ns",FALSE,TRUE)) %>% 
  dplyr::mutate(feature=ifelse(significant=="ns","",feature)) 
  
p0<-ggplot(plot_data)+
    geom_point(aes(x=coef,y=`-log(qval)`,color=significant))+
    ggrepel::geom_text_repel(aes(x=coef,y=`-log(qval)`),size=2,
                                 label = plot_data$feature,max.overlaps = 30,
                                 box.padding = unit(0.25, "lines"),
                                  hjust = 1)+
    ggtitle("M4 vs M1 | Species/Placebo")
fit_data$results %>%
   dplyr::left_join(tax_df) %>% 
  dplyr::select(-feature, -name) %>% 
  dplyr::relocate(Species,.before = metadata) %>%
  dplyr::arrange(pval) %>%  head() %>% knitr::kable()
file.remove("output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_placebo_Taxa.xlsx")
fit_data$results %>% 
  dplyr::left_join(tax_df) %>% 
  dplyr::select(-feature, -name) %>% 
  dplyr::relocate(Species,.before = metadata) %>% 
  xlsx::write.xlsx(.,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_placebo_Taxa.xlsx",sheetName = "Species")
p0
### Genus Level
input_data <- x.2.0.species %>% tax_glom(.,taxrank="Genus",NArm = F) %>% otu_table() %>% t()
input_metadata<-x.2.0.species %>% tax_glom(.,taxrank="Genus",NArm = F) %>% phyloseq::sample_data() %>% data.frame()
rownames(input_metadata)<-input_metadata$SampleID
tax_df<-tax_table(x.2.0.species %>% 
                    tax_glom(.,taxrank="Genus",NArm = F)) %>% 
  data.frame() %>%  dplyr::select(Genus) %>% 
  tibble::rownames_to_column("feature")
# rownames(input_metadata)
if( file.exists("output/Deliverables/Goal2/DifferentialAbundance/maaslin/genus_placebo.rds")){
  fit_data<-readRDS("output/Deliverables/Goal2/DifferentialAbundance/maaslin/genus_placebo.rds")
}else{
  suppressWarnings(fit_data <- Maaslin2::Maaslin2(input_data=input_data,input_metadata=input_metadata,output="output/Deliverables/Goal2/DifferentialAbundance/maaslin/genus_Placebo",fixed_effects = c("Timepoint"),random_effects = c("Host_name"),cores=4)) ### No siginifcant hits
   saveRDS(fit_data,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/genus_placebo.rds")
}
fit_data$results %>% 
  dplyr::left_join(tax_df) %>% 
  dplyr::select(-feature, -name) %>% 
  dplyr::relocate(Genus,.before = metadata) %>% 
  xlsx::write.xlsx(.,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_placebo_Taxa.xlsx",sheetName = "Genus",append=T)
```

## Functional Analysis

### MaasLin2

One of the advantages of using metagenomic sequencing is the possibility to profile gene abundance in addition to taxonomical composition. this is done using HUMANN3 software. Briefly, this software performs the analysis in three stages:

  * Detection of the bacterial species that are present in the sample above threshold.
  * Download of full genomes of detected species and indexes of the sample-specific genomes and gene annotation. In this manner, we obtain a table of relative abundances for UniRef Gene families that are annotated using KEGG and eggNOG ontologies.
  * Read mapping to sample-specific full-genome. Quantification of gene relative abundance and annotation to pathways if possible using MetaCyc.
  
From these analysis, we'll use both MetaCYC pathway relative abundance and KEGG Ortholog groups relative abundance quantification to compare sample groups. We run MaasLin2 algorithm both at the MetaCyc pathway and UniRef levels using standard TSS normalization and log transformation. Note thata very high number of gene function features are being tested. No significant hits were found for Timepoint within the Probiotic nor the Placebo Group when using BH corrected q.values.

*Deliverables: DifferentialAbundance/maaslin/M4_vs_M1_probiotic_function.xlsx, DifferentialAbundance/maaslin/M4_vs_M1_probiotic_function.xlsx*
 
#### Probiotic group

There are several Pathways that are either enriched or depleted at M4 in the Probiotic group, when using uncorrected p-values:

```{r functional analysis chunk 1,include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F,eval=T}
suppressMessages(require(dplyr))
suppressMessages(require(phyloseq))
suppressMessages(require(lefser))
suppressMessages(require(ggplot2))
suppressMessages(require(patchwork))
suppressMessages(require(Maaslin2))

set.seed(1234)

ps_metaphlan<-readRDS("data/processed/ps_metaphlan_goal2.rds") %>% 
  phyloseq::subset_samples(Product=="848590-FR80-036-003")

### Prepare input_data, 
input_data<-read.delim("data/raw/FunctionalAnnotation/HUMANN3/All_pathabun_relab.tsv")
colnames(input_data)[1]<-"Pathway"
colnames(input_data)<-gsub("_Abundance","",colnames(input_data))
colnames(input_data)<-gsub("X","",colnames(input_data))
input_data<-input_data %>% dplyr::filter(! grepl("s__",Pathway)) %>% 
  dplyr::filter(! grepl("UNINTEGRATED",Pathway)) %>% 
  dplyr::filter(! grepl("UNMAPPED",Pathway))
rownames(input_data)<-input_data$Pathway
input_data$Pathway<-NULL

input_data<-input_data[,phyloseq::sample_names(ps_metaphlan)]

### Prepare metadata
input_metadata<-phyloseq::sample_data(ps_metaphlan) %>% data.frame()
rownames(input_metadata)<-input_metadata$SampleID
if( file.exists("output/Deliverables/Goal2/DifferentialAbundance/maaslin/pathways_probiotic.rds")){
  fit_data<-readRDS("output/Deliverables/Goal2/DifferentialAbundance/maaslin/pathways_probiotic.rds")
}else{
  suppressMessages(fit_data <- Maaslin2::Maaslin2(input_data=input_data,input_metadata=input_metadata,output="output/Deliverables/Goal2/DifferentialAbundance/maaslin/function/pathways/probiotic",fixed_effects = c("Timepoint"),random_effects = c("Host_name"),cores = 4) )### No siginifcant hits
  saveRDS(fit_data,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/pathways_probiotic.rds")
}
file.remove("output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_probiotic_function.xlsx")
fit_data$results %>% 
  xlsx::write.xlsx(.,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_probiotic_function.xlsx",sheetName = "MetaCyc")
fit_data$results %>%
  dplyr::arrange(pval) %>% 
  dplyr::select(-name,-metadata) %>% 
  head(10) %>% 
  knitr::kable()

### Prepare input_data, GENE Families
input_data<-read.delim("data/raw/FunctionalAnnotation/HUMANN3/All_genefam_cpm_kegg.tsv")
colnames(input_data)[1]<-"Gene.Family"
colnames(input_data)<-gsub("_Abundance.RPKs","",colnames(input_data))
colnames(input_data)<-gsub("X","",colnames(input_data))
input_data<-input_data %>% dplyr::filter(! grepl("s__",Gene.Family)) %>% 
  dplyr::filter(! grepl("UNINTEGRATED",Gene.Family)) %>% 
  dplyr::filter(! grepl("UNMAPPED",Gene.Family)) %>% 
  dplyr::filter(! grepl("unclassified",Gene.Family))
rownames(input_data)<-input_data$Gene.Family
input_data$Gene.Family<-NULL
input_data<-input_data[,phyloseq::sample_names(ps_metaphlan)]
### Prepare metadata
input_metadata<-phyloseq::sample_data(ps_metaphlan) %>% data.frame()
rownames(input_metadata)<-input_metadata$SampleID

if( file.exists("output/Deliverables/Goal2/DifferentialAbundance/maaslin/genefamilies_probiotic.rds")){
  fit_data<-readRDS("output/Deliverables/Goal2/DifferentialAbundance/maaslin/genefamilies_probiotic.rds")
}else{
  suppressMessages(fit_data <- Maaslin2::Maaslin2(input_data=input_data,input_metadata=input_metadata,output="output/Deliverables/Goal2/DifferentialAbundance/maaslin/function/genes/probiotic",fixed_effects = c("Timepoint"),random_effects = c("Host_name"),cores = 4,min_prevalence = 0.4)) ### No siginifcant hits
   saveRDS(fit_data,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/genefamilies_probiotic.rds")
}
fit_data$results %>% 
  xlsx::write.xlsx(.,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_probiotic_function.xlsx",sheetName = "KEGG",append=T)

plot_data<-fit_data$results %>% 
  dplyr::mutate('-log(qval)'=-log10(qval)) %>% 
  dplyr::mutate(significant=ifelse(qval<0.05,"q<0.05","ns")) %>% 
  dplyr::mutate(labels=ifelse(significant=="ns",FALSE,TRUE)) %>% 
  dplyr::mutate(feature=ifelse(significant=="ns","",feature)) 
  
p0<-ggplot(plot_data)+
    geom_point(aes(x=coef,y=`-log(qval)`,color=significant))+
    ggrepel::geom_text_repel(aes(x=coef,y=`-log(qval)`),size=2,
                                 label = plot_data$feature,max.overlaps = 30,
                                 box.padding = unit(0.25, "lines"),
                                  hjust = 1)+
    ggtitle("M4 vs M1 | Gene Family/Probiotic")
# fit_data$results %>% dplyr::arrange(pval) %>%  head() %>% knitr::kable()
p0
```

#### Placebo group

```{r functional analysis chunk 2,include=TRUE,echo=F, message=FALSE, warning=FALSE, paged.print=FALSE, tidy=F,eval=T}
suppressMessages(require(dplyr))
suppressMessages(require(phyloseq))
suppressMessages(require(lefser))
suppressMessages(require(ggplot2))
suppressMessages(require(patchwork))
suppressMessages(require(Maaslin2))

set.seed(1234)
ps_metaphlan<-readRDS("data/processed/ps_metaphlan_goal2.rds") %>% 
  phyloseq::subset_samples(Product=="848589-FR80-036-003")


### Prepare input_data, 
input_data<-read.delim("data/raw/FunctionalAnnotation/HUMANN3/All_pathabun_relab.tsv")
colnames(input_data)[1]<-"Pathway"
colnames(input_data)<-gsub("_Abundance","",colnames(input_data))
colnames(input_data)<-gsub("X","",colnames(input_data))
input_data<-input_data %>% dplyr::filter(! grepl("s__",Pathway)) %>% 
  dplyr::filter(! grepl("UNINTEGRATED",Pathway)) %>% 
  dplyr::filter(! grepl("UNMAPPED",Pathway))
rownames(input_data)<-input_data$Pathway
input_data$Pathway<-NULL

input_data<-input_data[,phyloseq::sample_names(ps_metaphlan)]

### Prepare metadata
input_metadata<-phyloseq::sample_data(ps_metaphlan) %>% data.frame()
rownames(input_metadata)<-input_metadata$SampleID
if( file.exists("output/Deliverables/Goal2/DifferentialAbundance/maaslin/pathways_placebo.rds")){
  fit_data<-readRDS("output/Deliverables/Goal2/DifferentialAbundance/maaslin/pathways_placebo.rds")
}else{
suppressMessages(fit_data <- Maaslin2::Maaslin2(input_data=input_data,input_metadata=input_metadata,output="output/Deliverables/Goal2/DifferentialAbundance/maaslin/function/pathways/placebo",fixed_effects = c("Timepoint"),random_effects = c("Host_name"),cores = 4) )### No siginifcant hits
  saveRDS(fit_data,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/pathways_placebo.rds")
}
file.remove("output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_placebo_function.xlsx")
fit_data$results %>% 
  xlsx::write.xlsx(.,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_placebo_function.xlsx",sheetName = "MetaCyc")
fit_data$results %>%
  dplyr::arrange(pval)  %>% 
  dplyr::select(-name,-metadata)%>% 
  head() %>% 
  knitr::kable()
### Prepare input_data, GENE Families
input_data<-read.delim("data/raw/FunctionalAnnotation/HUMANN3/All_genefam_cpm_kegg.tsv")
colnames(input_data)[1]<-"Gene.Family"
colnames(input_data)<-gsub("_Abundance.RPKs","",colnames(input_data))
colnames(input_data)<-gsub("X","",colnames(input_data))
input_data<-input_data %>% dplyr::filter(! grepl("s__",Gene.Family)) %>% 
  dplyr::filter(! grepl("UNINTEGRATED",Gene.Family)) %>% 
  dplyr::filter(! grepl("UNMAPPED",Gene.Family)) %>% 
  dplyr::filter(! grepl("unclassified",Gene.Family))
rownames(input_data)<-input_data$Gene.Family
input_data$Gene.Family<-NULL
input_data<-input_data[,phyloseq::sample_names(ps_metaphlan)]
### Prepare metadata
input_metadata<-phyloseq::sample_data(ps_metaphlan) %>% data.frame()
rownames(input_metadata)<-input_metadata$SampleID

if( file.exists("output/Deliverables/Goal2/DifferentialAbundance/maaslin/genefamilies_placebo.rds")){
  fit_data<-readRDS("output/Deliverables/Goal2/DifferentialAbundance/maaslin/genefamilies_placebo.rds")
}else{
  suppressMessages(fit_data <- Maaslin2::Maaslin2(input_data=input_data,input_metadata=input_metadata,output="output/Deliverables/Goal2/DifferentialAbundance/maaslin/function/genes/placebo",fixed_effects = c("Timepoint"),random_effects = c("Host_name"),cores = 4,min_prevalence = 0.4)) ### No siginifcant hits
  saveRDS(fit_data,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/genefamilies_placebo.rds")
}
fit_data$results %>% 
  xlsx::write.xlsx(.,file="output/Deliverables/Goal2/DifferentialAbundance/maaslin/M4_vs_M1_placebo_function.xlsx",sheetName = "KEGG",append=T)

plot_data<-fit_data$results %>% 
  dplyr::mutate('-log(qval)'=-log10(qval)) %>% 
  dplyr::mutate(significant=ifelse(qval<0.05,"q<0.05","ns")) %>% 
  dplyr::mutate(labels=ifelse(significant=="ns",FALSE,TRUE)) %>% 
  dplyr::mutate(feature=ifelse(significant=="ns","",feature)) 
  
p0<-ggplot(plot_data)+
    geom_point(aes(x=coef,y=`-log(qval)`,color=significant))+
    ggrepel::geom_text_repel(aes(x=coef,y=`-log(qval)`),size=2,
                                 label = plot_data$feature,max.overlaps = 30,
                                 box.padding = unit(0.25, "lines"),
                                  hjust = 1)+
    ggtitle("M4 vs M1 | Gene Family/Placebo")
# fit_data$results %>% dplyr::arrange(qval) %>%  head() %>% knitr::kable()
p0
```




